### 2018-04-18 Physics Notes/Turning Points/Special relativity/Special Relativity.tex
Update of all files to shorten preamble
Tidied to work with all linux systems
Bertozzi Notes

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{blindtext}
\usepackage{textcomp}
\usepackage{pgfplots}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}
\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Physics - Turning Points}

\usepackage{tikz}
\usetikzlibrary{scopes}

\usepackage{mathtools}

\newtagform{brackets}{[}{]}
\usetagform{brackets}

@@

@@

\end{tabular}

>>>>

\documentclass[12pt]{article}
\usepackage{../../../format}
\lhead{A Level Physics - Turning Points}

@@

{\renewcommand{\arraystretch}{2}

@@

\end{tabular}}
\section{Bertozzi's Experiment}
\includegraphics[width=12cm]{Bertozzi.jpg}
The experiment was set out to determine the variation of the kinetic energy of an electron, based on derived measurements.\\
Electrons were accelerated and fired across a gap to an aluminium plate.\\
Electrons accelerated from rest, through a known P.D.\\
Gain kinetic energy = eV (Known value)\\
Calculate speed from $v=\frac{d}{t}$ (d=8.4m)\\
As the bunch of electrons collided with the plate, the electrons give up their energy and the plate changes its temperature.\\
Knowing the specific heat capacity, the energy can be determined
$$E=mc\Delta\theta$$
For a known number of electrons (n) the kinetic energy of one electron could be calculated
$$E=\frac{mc\Delta\theta}{n}$$
